Real-Time Systems

### 2013-12-16 beamer/dit-paper-presentation.tex
further modification to lowercase stuff
SBESC version of DIT paper presentation

	\begin{frame}{Model}
  \begin{block}{Real-Time Systems}
  Systems with real-time constraints. (e.g. ABS, VOD, etc)
  \end{block}
  \textbf{Model:} $\tau$ set of $n$ tasks $\tau_i = (O_i, C_i, D_i, T_i)$ generating jobs $J_{i,j}$
      \begin{itemize}
      \item $O_i$ : arrival of the first job
      \item $C_i$ : execution time
      \item $D_i$ : relative deadline
      \item $T_i$ : time between two job arrivals
    \end{itemize}

@@

        \begin{block}{Feasibility by a scheduling policy}
        A task set is said to be \textbf{schedulable by a given scheduling policy} if every job in the task set completes before its deadline is reached when using this scheduling policy.
        \end{block}

        In the uniprocessor case, the EDF (Earliest Deadline First) scheduling policy is optimal, any feasible task set is EDF-schedulable.
	\end{frame}

@@

        \begin{itemize}
            \item A region of $\mathbb{N}_0^n$ such as the C-space is described by a set of parametric linear constraints
            \item An efficient description allows us to quickly  whether a system whose $O_i$, $T_i$ and $D_i$ values are known will be feasible on a given platform (which gives the $C_i$).
        \end{itemize}

@@

    \begin{frame}{Demand-bound function feasibility test}
        \begin{block}{Demand-bound function}
            The \textbf{demand-bound function (DBF)} \cite{baruah1999generalized,
        baruah1990algorithms}
            defined for a task set $\tau$ in a time interval $[t_1, t_2]$, denoted $\dbf{t_1, t_2}$, is
            the maximal cumulated execution time of jobs of $\tau$ contained in the
            closed interval $[t_1, t_2]$.
        \end{block}
        $$\dbf{t_1, t_2} = \sum_{i=1}^{n} n_i(t_1, t_2) \, C_i$$
        where $n_i(t_1, t_2)$ is the number of jobs of task $\tau_i$ whose arrival times
        and deadlines are both in the closed interval $[t_1, t_2]$.

@@

    \begin{itemize}
        \item Every constraint is linear in the $C_i$ values
        \item Every constraint is necessary
        \item Their conjunction is sufficient
        % \pause
        \item But we have an infinite number of constraints!
        \item $\Rightarrow$ Removing redundancy
    \end{itemize}
    \end{frame}

    \begin{frame}{Removing redundancy for synchronous system}

@@

	In the article, we
    \begin{itemize}
        \item Introduce the notion of \textbf{first periodic DIT (FPDIT)} as a generalization of the notion of DIT
        \item Provide an algorithm to find an efficient description of the C-space for any periodic system
        \item Quantify the feasibility gain of random offsets in terms of C-space volume ratio.
    \end{itemize}

@@

    \begin{frame}{Finding the FPDIT value - Gauss's Algorithm}
        For given values of $a_i$, if the periods are pairwise coprime, the value of a DIT is given by:

@@

    \begin{frame}{Non-pairwise co-prime moduli}
        If the periods are non-pairwise co-prime, the system has a DIT for given values of $a_i$ if and only if the following condition is respected:
        \[
            a_i + O_i \equiv a_j + O_j \; (\operatorname{mod} \; \operatorname{gcd}(T_i,
            T_j)) \; \forall i,j
        \]

        Then each equation $t_d \equiv x \; (\operatorname{mod} \; p)$ with $p = p_1^{b_1} \cdots p_k^{b_k}$ (where each $p_i$ is prime), can be replaced by the system:

       \[
            \begin{array}{l}
                \left\{
                    \begin{array}{l}
                         t_d \equiv x \; (mod \; p_1^{b_1}) \\
                         \cdots \\
                         t_d \equiv x \; (mod \; p_k^{b_k})
                    \end{array}
                \right.
            \end{array}
        \]

        Equations with the same $p_i$ can be replaced by only the one of highest $b_i$. The new system now has pairwise co-prime moduli.

@@

\section{C-space of asynchronous system}

@@

        As in the synchronous case,
        \begin{itemize}
            \item Every constraint is necessary
            \item Their conjunction is sufficient
            \item Most of them are redundant.
        \end{itemize}
        However the method used to remove redundancies will be different.
	\end{frame}

@@

    We can define the redundancy of a linear constraint $C \cdot X \leqslant d$ with regards to a set of $k$ linear constraints $A \cdot X \leqslant B$ as the following Integer Linear Problem (ILP):

    \begin{columns}[c]
        \column{0.1\textwidth}
        \column{0.3\textwidth}

        \begin{center}
        $z = \max \left( C \cdot X \right)$

        s.t.

        $
        \begin{array}{rcc}
          A \cdot X &\leq & B \\
          C \cdot X &\leq & d + 1
        \end{array}
        $
        \end{center}

        \column{0.1\textwidth}

        \begin{center}with\end{center}
        \[
          \begin{array}{ccc}
            A & : & [n,k] \text{ matrix}\\
            B \; \text{and} \; C & : & [n,1] \text{ matrix}\\
            X & : & [1,n] \text{ matrix}\\
            d & : & \text{integer}
          \end{array}
        \]
    \end{columns}
        \begin{itemize}
            \item If $z = d + 1$, the constraint is redundant
            % \item Can be solved with a branch-and-bound approach
            \item Complexity (one test): exponential in the size of the set
            \item Each constraint of the set must be tested
        \end{itemize}

        \begin{algorithm}[H]
            \caption{Removing redundant constraints}
            \label{alg:pruneCspace}
          \begin{algorithmic}[1]
            \STATE $CSPACE$ : set of constraints
            \STATE $S \leftarrow \emptyset$
            \STATE \COMMENT{$1^{st}$ pass: test each $cstr$ against previous ones}
            \FOR{$cstr$ \textbf{in} $CSPACE$}
              \IF {$cstr$ is not redundant w.r.t. $S$}
                \STATE $S.push(cstr)$
              \ENDIF
            \ENDFOR
            \STATE \COMMENT{$2^{nd}$ pass: test remaining $cstr$ against every other}
            \FOR{$cstr$ \textbf{in} $S$}
              \STATE $cstr$ = $S.pop()$
              \IF {$cstr$ is not redundant w.r.t. $S$}
                \STATE $S.push(cstr)$
              \ENDIF
            \ENDFOR
            \RETURN{S}
            \end{algorithmic}
        \end{algorithm}

@@

@@

    We remove the remaining redundancies with the ILP:
    $$
        \left\{
            \begin{array}{cccccc}
                & & & C_2 & \leqslant & 2 \\
                C_1 & + & & C_2 & \leqslant & 7
            \end{array}
        \right.
    $$

@@

    \begin{itemize}
        \item Further ways of reducing redundancy before applying the simplex
        \item Other metrics to quantify the quality of the C-space
        \item Extension to multiprocessor scheduling
    \end{itemize}

>>>>

	\begin{frame}{Model}
  \begin{block}{Real-Time Systems}
  Systems with timeliness constraints. (e.g. ABS, VOD, etc)
  \end{block}
  \textbf{Model:} $\tau$ set of $n$ tasks $\tau_i = (O_i, C_i, D_i, T_i)$ generating jobs $J_{i,j}$
      \begin{itemize}
      \item $O_i$ : arrival of the first job
      \item $C_i$ : worst-case execution time (WCET)
      \item $D_i$ : relative deadline
      \item $T_i$ : time between two job arrivals
    \end{itemize}

@@

        % \begin{block}{Feasibility by a scheduling policy}
        % A task set is said to be \textbf{schedulable by a given scheduling policy} if every job in the task set completes before its deadline is reached when using this scheduling policy.
        % \end{block}

        In the uniprocessor case, the EDF (Earliest Deadline First) scheduling policy is optimal, any feasible task set is correctly scheduled by EDF.
	\end{frame}

@@

        \begin{itemize}
            \item A region of $\mathbb{N}_0^n$ such as the C-space is described by a set of parametric linear constraints on the $C_i$.
            \item An efficient description allows us to decide whether a system whose $O_i$, $T_i$ and $D_i$ values are known will be feasible on a given platform (which gives the $C_i$).
        \end{itemize}

@@

    \begin{frame}{Demand-bound function feasibility test}
        \begin{block}{Demand-bound function}
            The \textbf{demand-bound function (DBF)} \cite{baruah1999generalized,
        baruah1990algorithms}
            of a task set $\tau$, denoted $\dbf{t_1, t_2}$, is
            the maximal cumulated execution time of jobs of $\tau$ contained in the
            closed interval $[t_1, t_2]$.
        \end{block}
        $$\dbf{t_1, t_2} = \sum_{i=1}^{n} n_i(t_1, t_2) \, C_i$$
        where $n_i(t_1, t_2)$ is the number of jobs of $\tau_i$ in the interval $[t_1, t_2]$.

@@

    \begin{itemize}
        \item Every constraint is linear in the $C_i$ values.
        \item We have an infinite number of constraints!
        \item Every constraint is a necessary condition of feasibility.
        \item Their conjunction is a sufficient condition of feasibility.
        % \pause
        \item $\Rightarrow$ We must find a way of removing redundancies in the constraints.
    \end{itemize}
    \end{frame}

    \begin{frame}{Removing redundancy for synchronous systems}

@@

	In the article, we
    \begin{itemize}
        \item Introduce the notion of \textbf{first periodic DIT (FPDIT)} as a generalization of the notion of DIT
        \item Provide an algorithm to find an efficient description of the C-space for any periodic constrained deadline systems
        \item Quantify the feasibility gain of random offsets in terms of C-space volume ratio.
    \end{itemize}

@@

    \begin{frame}{Finding the FPDIT value - Gauss's Algorithm}
        For given values of $a_i$, if the periods are pairwise coprime, the value of a DIT is given by :

@@

    \begin{frame}{Non-pairwise co-prime moduli}
        If the periods are non-pairwise co-prime, the system has a DIT for given values of $a_i$ if and only if the following condition is respected:
        \[
            a_i + O_i \equiv a_j + O_j \; (\operatorname{mod} \; \operatorname{gcd}(T_i,
            T_j)) \; \forall i,j
        \]
		The CRP is then solved by constructing an equivalent system with pairwise co-prime moduli.\\

		In the asynchronous case, it is thus possible to have systems where no FPDIT exists.
        %Then each equation $t_d \equiv x \; (\operatorname{mod} \; p)$ with $p = p_1^{b_1} \cdots p_k^{b_k}$ (where each $p_i$ is prime), can be replaced by the system:

       %\[
       %     \begin{array}{l}
       %         \left\{
       %             \begin{array}{l}
       %                  t_d \equiv x \; (mod \; p_1^{b_1}) \\
       %                  \cdots \\
       %                  t_d \equiv x \; (mod \; p_k^{b_k})
       %             \end{array}
       %         \right.
       %     \end{array}
       % \]

        %Equations with the same $p_i$ can be replaced by only the one of highest $b_i$. The new system now has pairwise co-prime moduli.

@@

\section{C-space of asynchronous systems}

@@

        As in the synchronous case,
        \begin{itemize}
            \item Every constraint is a necessary condition.
            \item Their conjunction is a sufficient condition.
            \item Most of them are redundant.
        \end{itemize}
        However the method used to remove redundancies will be different.
	\end{frame}

@@

@@

    We can define the redundancy of a linear constraint $DBF' \cdot C \leqslant t_2 - t_1$ with regards to the set of $k$ linear constraints $DBF \cdot C \leqslant T$ as the following Integer Linear Problem (ILP):

    \begin{columns}[c]
        \column{0.5\textwidth}

        % \begin{center}
        $z = \max \left( DBF' \cdot C \right)$

        s.t. $DBF  \cdot C \leq T$

        %$
        % \begin{array}{ccccc}
        % DBF  & \cdot & C &\leq & T \\
        % DBF' & \cdot & C &\leq & t_2 - t_1 + 1
        % \end{array}
        %$
        % \end{center}

        \column{0.4\textwidth}

        % \begin{center}with\end{center}
        \[
          \begin{array}{ccc}
            DBF & : & [n,k] \text{ matrix}\\
            DBF' \; \text{and} \; T & : & [n,1] \text{ matrices}\\
            C & : & [1,n] \text{ matrix}\\
            t_2 \; \text{and} \; t_1 & : & \text{integers}
          \end{array}
        \]
    \end{columns}
        \begin{itemize}
            \item If $z \leqslant t_2 - t_1$, the constraint is redundant
            % \item Can be solved with a branch-and-bound approach
            \item Complexity (one test): exponential in the size of the set
            \item Each constraint of the set must be tested
        \end{itemize}

        \begin{algorithm}[H]
            \caption{Removing redundant constraints}
            \label{alg:pruneCspace}
          \begin{algorithmic}[1]
            \STATE $CSPACE$ : set of constraints
            \STATE $S \leftarrow \emptyset$
            \STATE \COMMENT{$1^{st}$ pass: test each $cstr$ against previous ones}
            \FOR{$cstr$ \textbf{in} $CSPACE$}
              \IF {$cstr$ is not redundant w.r.t. $S$}
                \STATE $S.push(cstr)$
              \ENDIF
            \ENDFOR
            \STATE \COMMENT{$2^{nd}$ pass: test remaining $cstr$ against every other}
            \FOR{$cstr$ \textbf{in} $S$}
              \STATE $cstr$ = $S.pop()$
              \IF {$cstr$ is not redundant w.r.t. $S$}
                \STATE $S.push(cstr)$
              \ENDIF
            \ENDFOR
            \RETURN{S}
            \end{algorithmic}
        \end{algorithm}
    \end{frame}

	\begin{frame}{Redundancy removal summary}

		To summarize, a finite number of constraints is given by applying the DBF test to intervals:
		\begin{itemize}
			\item beginning at a job arrival,
			\item ending at a job deadline,
			\item strictly contained in
			\begin{itemize}
				\item $[t_d, t_d + H]$ if there exists a FPDIT at $t_d$
				\item $[O_{max}, O_{max} + 2 \cdot H]$ otherwise
			\end{itemize}
		\end{itemize}

		Remaining redundancies are removed with a general ILP approach.

@@

    We remove the remaining redundancies with the ILP approach:
    $$
        \left\{
            \begin{array}{cccccc}
                & & & C_2 & \leqslant & 2 \\
                C_1 & + & & C_2 & \leqslant & 7
            \end{array}
        \right.
    $$

@@

    \begin{itemize}
        \item Further ways of reducing redundancy before applying the ILP approach
        \item Other metrics to quantify the quality of the C-space
        \item Extension to multiprocessor scheduling
    \end{itemize}
